\documentclass[main.tex]{subfiles}

\begin{document}
\begin{rmk}[Naive Characterisation of Continuity]
  
  Let $X, Y$ be topological spaces, $f : X \to Y$ a map of sets. 
  Suppose for a moment that we have the notion of 
  what it means for $f$ to be \emph{continuous}.
  Then we would hope that the following are equivalent : 
  \begin{enumerate}
    \item $f$ is a continuous.
    \item For all $x \in X$ and $\al : \N \to X$,
    $\al \to x$ $\imp$
    $f \circ \al \to f(x)$.
  \end{enumerate}
  This is essentially true; we need to replace $\al$ with filters.
  So clearly, we need a way of ``taking the image of a filter''. 
  A nice thing about filters is that,
  whilst there is no canonical way of taking the 
  \emph{preimage of a sequence}, 
  this is possible for filters.
\end{rmk}

\begin{dfn}[Image Filter, Preimage Filter]

  Let $f : X \to Y$ be a map of sets, $\al \in \fil(X)$, $\be \in \fil(Y)$. 
  Then define the \emph{image of $\al$} and the \emph{preimage of $\be$}
  by \begin{align*}
    f \al &:= \set{V \subseteq Y \st \exists\,U \in \al, f U \subseteq V} \\
    f^{-1} \be &:= \set{f^{-1}U \subseteq X \st U \in \be}
  \end{align*}
\end{dfn}

\begin{prop}[Adjunction of Image and Preimage Filters]

  Let $f : X \to Y$ be a map of sets. 
  Then \begin{enumerate}
    \item $f : \fil(X) \to \fil(Y)$ and $f\inv : \fil(Y) \to \fil(X)$
    are order preserving.
    \item For $\al \in \fil(X)$ and $\be \in \fil(Y)$, 
    $\al \to f^{-1}\be \iff f\al \to \be$.
  \end{enumerate}
\end{prop}
\begin{proof} 
  Easy. 
\end{proof}

\begin{prop} [Characterisation of Continuity]
  
  Let $X, Y$ be topological spaces, $f : X \to Y$ a map of sets. 
  Then the following are equivalent : 
  \begin{enumerate}
    \item (Standard) For all opens $U \subs Y$, $f\inv U$ is open in $X$.
    \item (Filters) For all $x \in X$ and $\al \in \fil(X)$,
    $\al \to x$ implies $f\al \to f(x)$.
    \item (Neihbourhood Filters Suffice)
    For all $x \in X$, $f N(x) \to N(f(x))$.
  \end{enumerate}
  We call $f$ \emph{continuous}, or a \emph{morphism of topological spaces},
  when it satisfies any (and thus all) of the above. 
\end{prop}
\begin{proof}
  % $(1\imp 2)$
  % Let $\al \to x \in X$.
  % Let $V \in N(f(x))$.
  % Then $f^{-1}V \in N(x) \subseteq F$ by continuity of $f$,
  % and $f f^{-1} V \subseteq V$.
  % So $N(f(x)) \subseteq f F$.
% 
  % $(2\imp 3)$ Clear. 
% 
  % $(2\imp 1)$ 
  % Let $U \in Open(Y)$.
  % Then for all $x \in f^{-1}U$,
  % $fN(x)$ converges to $f(x)$ implies $U \in fN(x)$.
  % So there exists $U_x \in N(x)$, $fU_x \subseteq U$.
  % It follows that $f^{-1}U = \bigcup_{x \in f^{-1}U} U_x$, 
  % which is open. 

  $(1 \imp 2)$
  Let $V \in N(f(x))$. Then $f\inv V \in N(x)$.
  Then $\al \to f\inv V$ implies $f \al \to f f\inv V$ implies $f \al \to V$.

  $(2 \iff 3)$ Clear. 
  $(3 \imp 1)$
  It suffices that for all $x \in f\inv U$, $f\inv U \in N(x)$.
  Well, for $x \in f\inv U$, 
  $fN(x) \to N(f(x)) \to U$ implies $fN(x) \to U$,
  which implies $N(x) \to f\inv U$ as desired. 
\end{proof}

\begin{dfn}[Category of Topological Spaces]
  
  Define $\TOP$, the \emph{category of topological spaces}, by setting :
  \begin{itemize}
    \item objects of $\TOP$ to be topological spaces.
    \item for two $X,Y \in \TOP$, the set of 
    morphisms $\TOP(X,Y)$ to be morphisms of topological spaces. 
    \item for $X \in \TOP$, $\id{X}$ is automatically continuous. 
    \item the composition of morphisms of topological spaces 
    is easily seen to be another morphism of topological spaces. 
  \end{itemize}
\end{dfn}

\end{document}